\documentclass{article}

\usepackage{caption}
\usepackage{booktabs}

\usepackage{silence}
\WarningFilter{latex}{You have requested package}

\usepackage{lib/myIncludeImg}
\usepackage{lib/defaultReportSettings}
\usepackage{lib/myTitlePage}
\usepackage{lib/myFigure}
\usepackage{lib/customCppLstling}

\begin{document}
	\def \reportSubj{Multiple inheritance}
	\myTitlePage{OOP}{Terman Emil FAF161}[M. Kulev][\reportSubj][5]

	\section{Objectives}
		\begin{itemize}
			\item studierea regulilor de determinare a moştenirii multiple.
			\item studierea avantajelor şi neajunsurilor moştenirii multiple.
			\item probleme legate de utilizarea moştenirii multiple.
		\end{itemize}

	\section{Main notions of theory and used methods}
		\par Multiple Inheritance is a feature of C++ where a class can inherit from more than one classes.

		\par \textbf{The diamond problem} occurs when two superclasses of a class have a common base class. For example, in the following diagram, the TA class gets two copies of all attributes of Person class, this causes ambiguities.

	\section{Task}
		Să se creeze, o ierarhie de moştenire: om - student, colaborator - practicant

	\section{Data analysis}
		\begin{itemize}
			\item the \textit{Human} class has a \textit{name} string.

			\item the \textit{Student} and \textit{Collaborator} \underline{virtualy} inherit from \textit{Humane}, because we have the \textbf{diamond} problem and we need to resolve the problem whith the Human constructor.

			\item both \textit{Student} and \textit{Collaborator} have a \textit{grade} field. Because they both have something with the same name, when \textit{Intern} inherits from both of them, we must also specify the class we are refering to.
		\end{itemize}

	\section{The actual code}
		\begin{center}

		\begin{minipage}{\textwidth}
			\includeCPPFile{../code/includes/Human.hpp}[Human.hpp]
		\end{minipage}

		\begin{minipage}{\textwidth}
			\includeCPPFile{../code/includes/Student.hpp}[Student.hpp]
		\end{minipage}

		\begin{minipage}{\textwidth}
			\includeCPPFile{../code/includes/Collaborator.hpp}[Collaborator.hpp]
		\end{minipage}

		\begin{minipage}{\textwidth}
			\includeCPPFile{../code/includes/Intern.hpp}[Intern.hpp]
		\end{minipage}

		\begin{minipage}{\textwidth}
			\includeCPPFile{../code/src/Intern.cpp}[Intern.cpp]
		\end{minipage}

		\begin{minipage}{\textwidth}
			\includeCPPFile{../code/src/main.cpp}[main.cpp]
		\end{minipage}

		\end{center}

	\section{Analysis of the results and conclusions}
		\begin{itemize}
			\item because multiple inheritance makes more problems than it solves, it is eliminated in more advanced languages, so it's not a necessary feature.

			\item it is useful in some particular cases, but mostly, we can workaround them by using composition.

			\item despite that, I think, it would be better if modern languages had this feature, because with it, we may find a more elegant solution to our problems.
		\end{itemize}
\end{document}